# Chapter 13 - Hotel Bookings

For this chapter, since I did some logistic regression in Python for Kaggle, lets try Rstan !

```{r}
# Load packages
library(bayesrules)
library(rstanarm)
library(bayesplot)
library(tidyverse)
library(tidybayes)
library(broom.mixed)
```


```{r}
data("hotel_bookings")
```

## Exercise 13.6 

### Proportion of the sample bookings were cancelled?
 %
```{r}
hotel_bookings %>%  
   select(is_canceled)  %>% summarize(fraction_cancelled = mean(is_canceled==1))
```


### Look at plots of each predictor vs `is_canceled`

The predictors the problem are `lead time` `previous_cancellations` `is_repeated_guest` and `average_daily_rate`

We care going to need to do some cuts


```{r}
hotel_bookings <- hotel_bookings %>% 
   select(is_canceled,lead_time, previous_cancellations, is_repeated_guest, average_daily_rate )
```
 
 


```{r}
hotel_bookings %>% summarise(across(where(is.numeric), mean))
```
```{r}
hotel_bookings %>% summarise(across(where(is.numeric), max))
```


```{r}
hotel_bookings %>% group_by(is_repeated_guest) %>% 
  summarize(cancel_rate = mean(is_canceled==1))
```

Looks like repeated guests are less likely to cancel


```{r}
hotel_bookings %>%
  mutate(lead_time_cut = cut(lead_time, breaks =10)) %>%
   group_by(lead_time_cut) %>% summarize(cancel_rate = mean(is_canceled==1)) %>%
  ggplot(aes(x= lead_time_cut, y= cancel_rate)) + 
    geom_point() + 
    theme(axis.text.x = element_text(angle=45, vjust =0.5))
```
 
 Longer lead times lead to more cancellations
 
```{r}
hotel_bookings %>%
  mutate(previous_cancel_cut = cut(previous_cancellations, breaks = c(-5,0,5,10,15,25,30))) %>%
   group_by(previous_cancel_cut) %>% summarize(cancel_rate = mean(is_canceled==1)) %>%
  ggplot(aes(x= previous_cancel_cut, y= cancel_rate)) + 
    geom_point() + 
    theme(axis.text.x = element_text(angle=45, vjust =0.5))
```
 
Previously cancelling many times is a very strong predictor.



```{r}
hotel_bookings %>%
  mutate(daily_rate_cut = cut(average_daily_rate, breaks = seq(-50,400,50))) %>%
   group_by(daily_rate_cut) %>% summarize(cancel_rate = mean(is_canceled==1)) %>%
  ggplot(aes(x= daily_rate_cut, y= cancel_rate)) + 
    geom_point() + 
    theme(axis.text.x = element_text(angle=45, vjust =0.5))
```

weak predictors, but higher rates lead to more cancellations (except for the very high!)
Note the odd 'free' hotels. 

```{r}
hotel_bookings %>%
  mutate(daily_rate_cut = cut(average_daily_rate, breaks = seq(-50,400,50))) %>%
   group_by(daily_rate_cut) %>% count

``` 

### Model choice

For the model we will use  `is_cancelled ~ lead_time + previous_cancellations + is_repeated_guest + average_daily_rate` with Binomial family and default logit link.

I will use weakly informative priors centered at zero, including for the centered intercept.



## Exercise 13.7 


                             
```{r}
cancel_model <- stan_glm(is_canceled ~ lead_time + previous_cancellations + is_repeated_guest + average_daily_rate,
                             data = hotel_bookings, family = binomial,
                             prior_intercept = normal(0,1,autoscale=TRUE),
                             prior = normal(0,1, autoscale=TRUE),
                             chains = 4, iter = 5000*2, seed = 84735 )
```


```{r}
prior_summary(cancel_model)
```
```{r}
mcmc_trace(cancel_model)
```

```{r}
mcmc_dens_overlay(cancel_model)
```


```{r}
proportion_cancel <- function(x){mean(x == 1)}

pp_check(cancel_model, nreps = 100,
         plotfun = "stat", stat = "proportion_cancel") + 
  xlab("probability of cancel")
```

Looks good. Now lets look at the model


```{r}
tidy(cancel_model, effects = "fixed", conf.int = TRUE, conf.level = 0.80)
```

The model is simply the logit of the linear model described above, not going to write it down though.
 
Note that these are log odds. to get odds;

```{r}
exp(posterior_interval(cancel_model,prob=.8))
```




Looks to me that all expect perhaps `is_repeated_guest` are statistically significant.

For lead time , each 10 days of lead time will cause about a 5% increase in odds of cancelling , so is not very strong
For previous cancellations, it is clear that having multiple previous cancellations is storng.
For repeated_guest,  being repeat guest means the odds are decreased by about half. 
Finally every 10 dollar increase in rate causes an increats of about 7% as well in the odds, so not very strong there either.




## Exercise 13.8

```{r}
classification_summary(model = cancel_model, data= hotel_bookings, cutoff = 0.5)
```

Lets do it by hand:




## Exercise 13.9