
Looking at the coffee ratings to decide if it is hierarchical or not. No intention to run any models.

```{r}
library(bayesrules)
library(tidyverse)
library(janitor)
```


```{r}
coffee_ratings <- coffee_ratings %>% filter(flavor > 5)
```

 
```{r}
ggplot(data = coffee_ratings) + geom_freqpoly(mapping = aes(x=flavor, color =species, y = ..density..))
```


```{r}
tabyl(coffee_ratings,country_of_origin,species)
```
From this we can see that there are only a few countries producing Robusta at all, and not very many batches are of that kind.  

So perhaps it would make sense to control for this , since for some countries the baseline probabiliy will be higher then for others (where it might be zero)

Let me try to see how the probability depends on country and flavor:


```{r}
coffee_ratings <- coffee_ratings %>%
   mutate(flavor_bin = cut(flavor, breaks = seq(6,9,.5))) 

test <- coffee_ratings %>% 
  group_by(flavor_bin, country_of_origin) %>%
  summarize(prob_robusta = mean(species == 'Robusta'),.groups='drop')

ggplot(data = test) + 
  geom_point(mapping=aes(x=flavor_bin, y = prob_robusta, color = country_of_origin))
```

Well there is just not a lot of data. Clearly baseline probability is zero for most, lets cut those out.

```{r}
countries_with_robusta = coffee_ratings %>% group_by(country_of_origin) %>% summarize(robusta_count = sum(species=='Robusta')) %>% filter(robusta_count > 0) %>% pull(country_of_origin)
```


```{r}
test2 <- coffee_ratings %>% filter(country_of_origin %in% countries_with_robusta )%>%
  group_by(flavor_bin, country_of_origin) %>%
  summarize(prob_robusta = mean(species == 'Robusta'),.groups='drop')

ggplot(data = test2) + 
  geom_point(mapping=aes(x=flavor_bin, y = prob_robusta, color = country_of_origin, shape=country_of_origin)) 

```



But on the other hand there is not a lot of data . 

